Semantic Textual Similarity using deep learning

### 2017-06-04 paper/main.tex
latex updated
Small fixes

\subsubsection{Model}
All features were preprocessed with StandardScaler\footnote{http://scikit-learn.org/stable/modules/generated/sklearn.preprocessing.StandardScaler.html}. For selection of best model we used nested cross validation. Both inner and outer CV used 5-Fold cross validation. We optimized following parameters of SVR model:

@@

\begin{table}
\caption{Averaged scores}
\label{tab:narrow-table}
\begin{center}
\begin{tabular}{cll}
\toprule
& R2 & Pearson correlation\\
\midrule
score &  & 0.7795 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

>>>>

\subsubsection{Model}
All features were preprocessed to zero mean and unit variance. For selection of best model we used nested cross validation, with Grid search in inner folds. Both inner and outer CV used 5-Fold. We optimized following parameters of SVR model:

@@

\begin{table}
\caption{Averaged scores}
\label{tab:narrow-table}
\begin{center}
\begin{tabular}{ccc}
\toprule
& R2 & Pearson\\
\midrule
score & 0.5898 & 0.7795 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
